### 2012-12-20 inst/examples/myers-exploration.Rmd
unique seeds for parallel computing

```{r }
yields <- 
  sfLapply(1:20, function(j){

x_0_observed <- allee + x_grid[5]
seed <- round(runif(1) * 1e6)
set.seed(seed)
print(seed)

## @knitr sim-obs
Tobs <- 50
x <- numeric(Tobs)
x[1] <- x_0_observed
for(t in 1:(Tobs-1))
  x[t+1] = z_g() * f(x[t], h=0, p=p)
qplot(1:Tobs, x)

@@

## @knitr gp-plot
true <- sapply(x_grid, f, 0, p)
est <- sapply(x_grid, f_alt, 0, p_alt)
models <- data.frame(x=x_grid, GP=tgp_dat$y, Parametric=est, True=true)
models <- melt(models, id="x")
names(models) <- c("x", "method", "value")
gp_plot <- ggplot(tgp_dat)  + geom_ribbon(aes(x,y,ymin=ymin,ymax=ymax), fill="gray80") +
  geom_line(data=models, aes(x, value, col=method), lwd=2, alpha=0.8) + 
  geom_point(data=obs, aes(x,y), alpha=0.8) + 
  xlab(expression(X[t])) + ylab(expression(X[t+1])) +
  scale_colour_manual(values=cbPalette)
print(gp_plot)

@@

## @knitr policy_plot
policies <- melt(data.frame(stock=x_grid, 
                            GP = x_grid[opt_gp$D[,1]], 
                            Parametric = x_grid[opt_estimated$D[,1]],
                            True = x_grid[opt_true$D[,1]]),
                 id="stock")
names(policies) <- c("stock", "method", "value")
policy_plot <- ggplot(policies, aes(stock, stock - value, color=method)) +
  geom_line(lwd=2, alpha=0.8) + 
  xlab("stock size") + ylab("escapement")  +
  scale_colour_manual(values=cbPalette)
print(policy_plot)

>>>>

```{r }
seed <- round(runif(20) * 1e6)
seed
yields <- 
  sfLapply(1:length(seed), 
           function(j){

x_0_observed <- allee + x_grid[5]
set.seed(seed[j])

## @knitr sim-obs
Tobs <- 50
x <- numeric(Tobs)
x[1] <- x_0_observed
for(t in 1:(Tobs-1))
  x[t+1] = z_g() * f(x[t], h=0, p=p)
data_plot <- qplot(1:Tobs, x) + ggtitle(paste("rep", j, "seed", seed))
print(data_plot)

@@

## @knitr gp-plot
true <- sapply(x_grid, f, 0, p)
est <- sapply(x_grid, f_alt, 0, p_alt)
models <- data.frame(x=x_grid, GP=tgp_dat$y, Parametric=est, True=true)
models <- melt(models, id="x")
names(models) <- c("x", "method", "value")
gp_plot <- ggplot(tgp_dat)  + geom_ribbon(aes(x,y,ymin=ymin,ymax=ymax), fill="gray80") +
  geom_line(data=models, aes(x, value, col=method), lwd=2, alpha=0.8) + 
  geom_point(data=obs, aes(x,y), alpha=0.8) + 
  xlab(expression(X[t])) + ylab(expression(X[t+1])) +
  scale_colour_manual(values=cbPalette) +
  ggtitle(paste("rep", j, "seed", seed))
print(gp_plot)

@@

## @knitr policy_plot
policies <- melt(data.frame(stock=x_grid, 
                            GP = x_grid[opt_gp$D[,1]], 
                            Parametric = x_grid[opt_estimated$D[,1]],
                            True = x_grid[opt_true$D[,1]]),
                 id="stock")
names(policies) <- c("stock", "method", "value")
policy_plot <- ggplot(policies, aes(stock, stock - value, color=method)) +
  geom_line(lwd=2, alpha=0.8) + 
  xlab("stock size") + ylab("escapement")  +
  scale_colour_manual(values=cbPalette) +
  ggtitle(paste("rep", j, "seed", seed))
print(policy_plot)
